This Final Degree Project has enabled the design of a modern and scalable network infrastructure based on the project specifications of the Consorcio de Aguas de la Zona Gaditana, focused on improving connectivity, security and the integration of services at its various sites. Through the use of technologies such as \texttt{SD-WAN}, IPv6 addressing, IP telephony and new generation firewalls.

\vspace{0.5cm}
During the development of the project, a detailed analysis of the technical requirements has been carried out and a star topology has been designed with a hierarchical network architecture of three layers (core, distribution and access). In addition, network devices have been selected, taking into account their performance, scalability, compatibility and cost.

\vspace{0.5cm}
The simulation of the network using \texttt{GNS3} has served to partially validate the proposed design, despite the technical limitations of the tool compared to real environments based on solutions such as \texttt{Cisco Meraki}.

\vspace{0.5cm}
Based on the work carried out, the following lines of work are proposed that can be used to improve the development and evolution of the project:
\begin{itemize}
  \item \textbf{Implementation of systems in the cloud:} implement the \texttt{FreePBX} PBX on the \texttt{Microsoft Azure} platform, taking advantage of the scalability and availability offered by the cloud. In addition, it is recommended to integrate  \texttt{Microsoft Sentinel} as an incident response platform, enabling centralised monitoring, detection and management of threats and security events related to IP telephony and other critical services.

  \item \textbf{Network configuration automation:} use tools such as \texttt{Ansible} or \texttt{Python} scripts to automate the deployment and configuration of routers and switches in the simulation.

  \item \textbf{Automation and advanced monitoring:} deploy complementary monitoring tools such as \texttt{Zabbix} for more detailed monitoring of services and devices not managed by \texttt{Meraki}.

  \item \textbf{Simulated performance evaluation and continuous improvement:} perform stress tests, traffic analysis and simulations of critical scenarios in virtual environments such as \texttt{GNS3}, in order to validate the proposed design, optimise its theoretical behaviour and detect possible weaknesses in the network architecture.
\end{itemize}